Practical implementation of a Hilbert space reduced-rank approximate Bayesian Gaussian process

### 2020-09-10 Paper/StanCon/poster/HSGP_StanCon_poster_landscape_full-content.tex
add StanCon poster folder

\documentclass[portrait,a1,final]{a0poster} % a0poster class sets the paper size
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[SCI]{aaltologo} % RGB, Coated, Uncoated
%\usepackage{times}
%\usepackage{lastpage}
\usepackage[center]{titlesec} % For changing the font on chapters, sections, etc.
\usepackage{amsmath,amsfonts,amssymb,amsbsy}
\usepackage{soul}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{amsmath}
%\usepackage{sectsty}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{url}
\usepackage{bm}
\usepackage[colorlinks,linkcolor=black,citecolor=black, urlcolor=blue,filecolor=blue]{hyperref}
\usepackage[left=0.5cm,right=0.5cm,bottom=1cm,top=1.5cm]{geometry} 
\usepackage{changepage}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{pbox}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage{setspace}

@@

%-- minipage for the logo at left side --%
\begin{minipage}[t]{0.17\linewidth} % logo
\vspace{1.3cm}

\begin{adjustwidth}{-0.3cm}{-0cm}
\includegraphics[scale=0.35]{\figpdfdir StanCon_logo.png}
\end{adjustwidth}

\end{minipage} % no empty line before the next begin
%-- minipage for title and authors --%
\begin{minipage}[t]{0.76\linewidth}
\vspace{0pt}

@@

\vspace{0.015\linewidth}

\normalsize{\textsf{\bfseries{Gabriel Riutort-Mayol$^{1}$ \;\;\; Paul-Christian Bürkner$^2$ \;\;\; Michael Riis Andersen$^{3}$ \;\;\; Arno Solin$^{2}$ \;\;\; Aki Vehtari$^{2}$}}}\\[2mm]

%\setstretch{1.2}
\textcolor{aaltoGray}{\textsf{\bfseries{\small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain 
\\
$^2$ Department of Computer Science, Aalto University, Finland
\\
$^3$ Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
\\[-2mm]
\footnotesize Contact: gabriuma@gmail.com, aki.vehtari@aalto.fi}}}

\end{minipage}
%-- minipage for the logo at rigth side --%
\begin{minipage}[t]{0.06\linewidth}
\vspace{0.7cm}

%\begin{adjustwidth}{-1cm}{-0cm}
{\centering \includegraphics[scale=0.8]{\figpdfdir aaltologo}}\\[0.5cm]
\includegraphics[scale=0.7]{\figpdfdir marca_UPV_secundaria_negro300.png}
%\end{adjustwidth}
\end{minipage}

@@

% Default font for text
\sffamily
%\small % Text size for a1 posters
\footnotesize % Text size for a1 posters

%------------ minipage for the main text ------------%
\begin{minipage}{1\linewidth} 
%------------ minipage for first column ------------%
%\hspace{0.001\textwidth}
\centering
\begin{minipage}[t]{0.48\linewidth}
\vspace{0pt}
\setlength{\parindent}{10mm} % Paragraph indent

@@

\hspace{45mm} $\ell=0.1$ \hspace{63mm} $\ell=0.3$ \hspace{64mm} $\ell=0.6$\\
\includegraphics[scale=0.57, trim = 0mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_1.pdf}
\includegraphics[scale=0.57, trim = 25.5mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_2.pdf}
\includegraphics[scale=0.57, trim = 25.5mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_3.pdf}

@@

\vspace{-0.6cm}
\section{Hilbert space approximate Gaussian process (HSGP)}
\vspace{-0.2cm}

@@

\end{minipage}% end minipage first column
\hspace{0.015\linewidth} 
%------------ minipage for second column ------------%
\begin{minipage}[t]{0.48\textwidth}
\vspace{0pt}
\setlength{\parindent}{10mm}

@@

\end{minipage} % End minipage second column
\hspace{0.02\linewidth} 
\end{minipage} % end minipage main text

>>>>

\documentclass[landscape,a1,final]{a0poster} % a0poster class sets the paper size
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[SCI]{aaltologo} % RGB, Coated, Uncoated
%\usepackage{times}
%\usepackage{lastpage}
\usepackage[center]{titlesec} % For changing the font on chapters, sections, etc.
\usepackage{amsmath,amsfonts,amssymb,amsbsy}
\usepackage{soul}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{amsmath}
%\usepackage{sectsty}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{url}
\usepackage{bm}
\usepackage[colorlinks,linkcolor=black,citecolor=black, urlcolor=blue,filecolor=blue]{hyperref}
\usepackage[left=0.5cm,right=0.5cm,bottom=1cm,top=1.5cm]{geometry} 
\usepackage{changepage}
\usepackage{amsthm}
\usepackage{tcolorbox}
\usepackage{pbox}
\usepackage{multicol}
\usepackage{nicefrac}
\usepackage{setspace}

@@

%-- minipage for the logo at left side --%
\begin{minipage}[t]{0.14\linewidth} % logo
\vspace{0.5cm}

%\begin{adjustwidth}{-1cm}{-0cm}
\includegraphics[scale=0.35]{\figpdfdir StanCon_logo.png}
%\end{adjustwidth}

\end{minipage} % no empty line before the next begin
%-- minipage for title and authors --%
\begin{minipage}[t]{0.50\linewidth}
\vspace{0.5cm}

@@

\vspace{5mm}
\normalsize{\textsf{\bfseries{Gabriel Riutort-Mayol$^{1}$ \;\;\; Paul-Christian Bürkner$^2$ \;\;\; Michael Riis Andersen$^{3}$ \;\;\; Arno Solin$^{2}$ \;\;\; Aki Vehtari$^{2}$}}}

\end{minipage}
%-- minipage for the logo at rigth side --%
\begin{minipage}[t]{0.22\linewidth}

\vspace{3mm}
\textcolor{aaltoGray}{\textsf{\bfseries{ \scriptsize
\begin{itemize}
	\setlength{\itemsep}{1mm}
	\item[] $^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain
\item[] $^2$ Department of Computer Science, Aalto University, Finland
\item[] $^3$ Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
\item[] Contact: gabriuma@gmail.com, aki.vehtari@aalto.fi
\end{itemize}
}}}

\end{minipage}
%-- minipage for the logo at rigth side --%
\hspace{15mm}
\begin{minipage}[t]{0.09\linewidth}
\vspace{1.5mm}

%\begin{adjustwidth}{-1cm}{-0cm}
\includegraphics[scale=0.8]{\figpdfdir aaltologo}
\raisebox{-5mm}{\includegraphics[scale=0.7]{\figpdfdir marca_UPV_secundaria_negro300.png}}
%\end{adjustwidth}
\end{minipage}

@@

% Default font for text
\sffamily
\small % Text size
%\footnotesize % Text size

%------------ minipage for the main text ------------%
\begin{minipage}{1\linewidth} 
%------------ minipage for first column ------------%
%\hspace{0.001\textwidth}
\centering
\begin{minipage}[t]{0.31\linewidth}
\vspace{0pt}
\setlength{\parindent}{10mm} % Paragraph indent

@@

\hspace{45mm} $\ell=0.1$ \hspace{63mm} $\ell=0.3$ \hspace{64mm} $\ell=0.6$\\
\includegraphics[scale=0.53, trim = 0mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_1.pdf}
\includegraphics[scale=0.53, trim = 25.5mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_2.pdf}
\includegraphics[scale=0.53, trim = 25.5mm 10mm 7mm 18mm, clip]{\figpdfdir func_samples_3.pdf}

@@

\end{minipage}% end minipage first column
\hspace{0.015\linewidth} 
%------------ minipage for second column ------------%
\begin{minipage}[t]{0.31\textwidth}
\vspace{0pt}
\setlength{\parindent}{10mm}

\vspace{0.3cm}
\section{Hilbert space approximate Gaussian process (HSGP)}
\vspace{-0.2cm}

@@

\end{minipage}% end minipage second column
\hspace{0.015\linewidth} 
%------------ minipage for third column ------------%
\begin{minipage}[t]{0.31\textwidth}
\vspace{0pt}
\setlength{\parindent}{10mm}

@@

\end{minipage} % End minipage third column
\hspace{0.02\linewidth} 
\end{minipage} % end minipage main text
